---
title: "ICD-11"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

CLIENT_ID <- Sys.getenv("CLIENT_ID")
CLIENT_SECRET <- Sys.getenv("CLIENT_SECRET")
```

To interact with ICD-11 you should first get your token:

```{r}
library(WHOicd)

#Substitute CLIENT_ID and CLIENT_SECRET by your credentials
token <- get_token(CLIENT_ID, CLIENT_SECRET)
```

## Autocoding text diagnosis

The function for automatically assigning an ICD-11 code from a diagnostic text is `icd11_autocode()`:

```{r}
#Auto code a diagnostic text such as `cerebrovascular accident`
code_results <- icd11_autocode(token, "Patient with cerebrovascular accident")
```

Code results is a list with multiple entries. In particular, `theCode` will give you the ICD-11 code identified:

```{r}
#Recover the code that matched
code_results |> retrieve("theCode")
```

The `matchScore` gives you a number between 0 and 1 specifying how good the match is. A perfect match is `1` while no-match would be `0`. 

```{r}
#Recover the code that matched
code_results |> retrieve("matchScore")
```

## Information on a code 

Once you have the matched code such as `r code_results |> retrieve("theCode")` from the previous section you can look for it with `icd11_codeinfo`. 

```{r}
#Recover the code that matched
code_info <- icd11_codeinfo(token, code = "8B20")
```

A lot of information is retrieved from the code:
```{r}
names(code_info)
```

In particular: 
* `parent` gives information of the chapter/section/block this code belongs to, 
* `@id` returns the URI which is the main indexing for the code in the online system, 
* `title` which is the name of the code, 
* `exclusion` which are the conditions not included, 
* `definition` provides a medical description of what it means, 
* `browseUrl` a link to the online website to search for it 
* `relatedEntitiesInMaternalChapter` are related codes in the chapter of maternal disease

You can use the retrieve function or access the elements from the list directly:

```{r}
code_info |> retrieve("title")
```

## Searching for codes

The `icd11_search()` function allows you to search for text and retrieve codes that contain that text. As an example, we can search for all codes containing or related to `malaria`:

```{r}
abortion_codes <- icd11_search(token, text = "malaria")
```

Which you can `retrieve()` the codes and titles of: 

```{r}
tibble::tibble(
  code = abortion_codes |> retrieve("theCode"),
  title = abortion_codes |> retrieve("title")
)
```

