---
title: "ICD-10"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

CLIENT_ID <- Sys.getenv("CLIENT_ID")
CLIENT_SECRET <- Sys.getenv("CLIENT_SECRET")
```

To interact with ICD-10 you should first get your token:

```{r}
library(WHOicd)

#Substitute CLIENT_ID and CLIENT_SECRET by your credentials
token <- get_token(CLIENT_ID, CLIENT_SECRET)
```

## Searching given a code 

The main function relating to ICD-10 is `icd10_search()` which searches for the titles and parents of codes, blocks of chapters. As an example, we can search for the following vector and obtain a `data.frame`: 

```{r}
#Search for code, specific code, chapter and block 
codes <- c("D60", "IX", "I10-I15")
icd10_search(token, codes)
```

If you only want to get the title of the current code/chapter/block you can use `icd10_title` which is faster as it requires less requests to the API:

```{r}
#Search for code, specific code, chapter and block 
codes <- c("D60", "IX", "I10-I15")
icd10_title(token, codes)
```

## Top-down search

Given a chapter you can also list all the blocks in a chapter

```{r}
icd10_blocks(token, chapter = "III")
```

As well as all of the chapters in a block:

```{r}
icd10_codes(token, block = "D55-D59")
```
The same command allows you to search inside a code:

```{r}
icd10_codes(token, block = "D55")
```

## Search for code in releases

Not all codes are available across releases. For example, the `C80.0` code was not in the `2008` release of the ICD-10. Hence if you are using that release you will not find it:

```{r}
icd10_search(token, "C80.0", release = 2008)
```

However you can use the `icd10_code_search_release` to search for a release containing that code:

```{r}
icd10_code_search_release(token, code = "C80.0")
```

and use one of those releases instead:

```{r}
icd10_search(token, "C80.0", release = 2016)
```

## Additional information on releases

The `icd10_releases` function lists all available ICD-10 releases

```{r}
icd10_releases(token)
```

The default is 2019. You can change it with the `release` parameter across all functions. 

To obtain the complete information on a certain release you can use the `icd10_release_info` function:

```{r}
icd10_release_info(token, release = 2016)
```

